Supporting 10 common mistakes article

### 2025-08-30 example_10m.Rmd
mistake 6

@@

df <- data.frame("up"=nups,"dn"=ndns,row.names=sizes)
df
plot(sizes,df$up,type="b",col="red",ylab="no. gene sets with FDR<0.05",xlab="gene list length")
lines(sizes,df$dn,type="b",col="blue")

plot(sizes,df$up,type="b",col="red",ylab="no. gene sets with FDR<0.05",xlab="gene list length",xlim=c(0,500))
lines(sizes,df$dn,type="b",col="blue")

>>>>

Will try FORA and mitch.

@@

df <- data.frame("up"=nups,"dn"=ndns,row.names=sizes)
df$tot <- df$up + df$dn
df

plot(sizes,df$up,type="b",col="red",ylab="no. gene sets with FDR<0.05",xlab="gene list length")
lines(sizes,df$dn,type="b",col="blue")

plot(sizes,df$up,type="b",col="red",ylab="no. gene sets with FDR<0.05",xlab="gene list length",
  xlim=c(0,500), ylim=c(0,125))
lines(sizes,df$dn,type="b",col="blue")

## Mistake 6 - combining up and downregulated genes into the same test.

```{r,mistake6a}

updn <- unique(c(up,dn))

fres_updn_bg <- fora(pathways=gsets, genes=updn, universe=bg, minSize = 5, maxSize = Inf)
fres_updn_bg <- subset(fres_updn_bg,padj<0.05)$pathway
length(fres_updn_bg)

length(fres_up_bg)
length(fres_dn_bg)
length(unique(c(fres_up_bg,fres_dn_bg)))

v1 <- list("up"=fres_up_bg,"dn"=fres_dn_bg,"both"=fres_updn_bg)
plot(euler(v1),quantities = list(cex = 2), labels = list(cex = 2))
